---
title: "Fars"
author: "Tom Cooper"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fars}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
#```{r global_options}
#knitr::opts_knit$set(root.dir = system.file("extdata",package="fars"))
#```

This package contains function for loading, summarizing and mapping data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. 

https://en.wikipedia.org/wiki/Fatality_Analysis_Reporting_System

## Usage 

### Load data for specific years

Returns a list, each element a data frame with data for individual year. 
Each row in data frame is a single fatal accident.
```{r}
fars::fars_read_years(c(2013,2014,2015))
```

### Summarize data for specific years

```{r}
fars::fars_summarize_years(c(2013,2014,2015))
```

### Map the accidents for a single year for specific state

Use the index from state.name as first parameter.

```
fars::fars_map_state(1,2013)
```
